---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# inciweb

<!-- badges: start -->
<!-- badges: end -->

The goal of `inciweb` is to allow users to programatically access data from the National Wildfire Coordinating Group's [Inciweb Incident Information System](https://inciweb.wildfire.gov/). It does so through one core function, `iw_get_incidents()`.

## Installation

You can install the development version of inciweb from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("oonuttlet/inciweb")
```

## Usage

This is a basic example which shows you how to get all incidents available on the Inciweb map:

```{r example, message=FALSE}
library(inciweb)
library(dplyr)

iw_get_incidents() |>
  glimpse()
```

The returned object includes all information available in the most recent update of the Inciweb database.

By default, `iw_get_incidents()` returns an `sf` object. This behavior can be changed using the argument `geometry = FALSE`. In this case, latitude and longitude columns are still returned; conversion to `sf` object is omitted.

```{r}
foo <- iw_get_incidents()
class(foo)

bar <- iw_get_incidents(geometry = FALSE)
class(bar)
```

## Getting Help

If you encounter an issue with accessing Inciweb data, please check to ensure the service is online. If the issue persists, please raise a new issue on [Github](https://github.com/oonuttlet/inciweb/issues).
